Measurement Bias from Address Aliasing

### 2014-05-25 paper.tex
Remove booktabs style from tables

% Typeset for Transactions on Architecture and Code Optimization
\documentclass[prodmode,acmtaco]{acmsmall}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{filecontents}
\usepackage{booktabs} % Only used for horizontal lines
\usepackage{tikz}
\usepackage{listings}
%\usepackage{caption}
\usepackage{mathtools}
\usepackage{underscore}
\usepackage{url}
\usepackage{lmodern} % Much clearer text

@@

% Detailed comparison between median and worst cases.
\begin{table}
  \tbl{Events with significant correlation to cycle count\label{tab:loopcorrelation}}{
    \pgfplotstabletypeset[
      int detect, % Output whole numbers for counter values
      col sep=comma,
      columns={Performance counter, Median, [index]3, [index]4},
      column type=r,
      columns/Performance counter/.style={
        string type, 
        column type=l,
        postproc cell content/.append code={
          \pgfkeysalso{@cell content=\perfctr{##1}}
        }
      },
      every head row/.style={
        output empty row,
        before row={\toprule
          Performance counter & Median & Spike 1 & Spike 2 \\
          },
        after row=\midrule,
      },
      every last row/.style={after row=\bottomrule}
    ]{bin/micro-kernel-comparison.csv}
  }
  \begin{tabnote}
    \Note{Note:}{Performance events that are obviously not indicative of any causal relationship are omitted, for example bus-cycles which will naturally vary with total cycle count.}
  \end{tabnote}
\end{table}

@@

% Table with detailed performance data, use estimated for O2 because it does not need as many columns (!)
\begin{table}[t]
  %\centering
  \label{tab:convstats}
  \renewcommand{\tabcolsep}{3pt} % Less padding between cells
  \tbl{Most interesting performance counters and correlation with cycle count for optimization O2, estimated cost accounting for constant overhead.}{
    \pgfplotstabletypeset[
      font=\footnotesize,
      int detect, % Output whole numbers for counter values
      col sep=comma,
      columns={Performance counter, Correlation, 0, 2, 4, 8},
      column type=r,
      columns/Performance counter/.style={
        string type, 
        column type=l,
        postproc cell content/.append code={
          \pgfkeysalso{@cell content=\perfctr{##1}}
        }
      },
      columns/Correlation/.style={
        fixed,
        fixed zerofill,
        precision=2
      },
      every head row/.style={
        output empty row,
        before row={\toprule
          Performance counter & $r$ & 0 & 2 & 4 & 8 \\
          },
        after row=\midrule,
      },
      every last row/.style={after row=\bottomrule}
    ]{bin/conv-default-o2.estimate.csv}
  }
\end{table}

@@

% Removed some data here, too much info
\begin{table*}[t]
  \centering
  \label{tab:mallocompare}
  %\renewcommand{\tabcolsep}{4pt} % Less padding between cells
  \tbl{Addresses returned by different heap allocators when allocating pairs of equally sized buffers.}{
    \pgfplotstabletypeset[
      font=\footnotesize,
      col sep=comma,
      string type,
      columns={Allocation, 64, 5120, 1048576},
      column type=r,
      columns/Allocation/.style={
        string type, 
        column type=l
      },
      every head row/.style={
        output empty row,
        before row={\toprule
           & 64 B & 5,120 B & 1,048,576 B \\
          },
        after row=\midrule,
      },
      every odd row/.style={after row=\midrule},
      every last row/.style={after row=\bottomrule}
    ]{bin/malloc-comparison.csv}
  }
\end{table*}

>>>>

% Typeset for Transactions on Architecture and Code Optimization
\documentclass[prodmode,acmtaco]{acmsmall}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{filecontents}
%\usepackage{booktabs} % Only used for horizontal lines
\usepackage{tikz}
\usepackage{listings}
%\usepackage{caption}
\usepackage{mathtools}
\usepackage{underscore}
\usepackage{url}
\usepackage{lmodern} % Much clearer text

@@

% Detailed comparison between median and worst cases.
\begin{table}
  \tbl{Events with significant correlation to cycle count\label{tab:loopcorrelation}}{
    \pgfplotstabletypeset[
      int detect, % Output whole numbers for counter values
      col sep=comma,
      columns={Performance counter, Median, [index]3, [index]4},
      column type=r,
      columns/Performance counter/.style={
        string type, 
        column type=l,
        column type/.add={|}{},
        postproc cell content/.append code={
          \pgfkeysalso{@cell content=\perfctr{##1}}
        }
      },
      every head row/.style={
        output empty row,
        before row={\hline
          Performance counter & Median & Spike 1 & Spike 2 \\
        },
        after row=\hline\hline
      },
      every last row/.style={after row=\hline},
      every last column/.style={column type/.add={}{|}}
    ]{bin/micro-kernel-comparison.csv}
  }
  \begin{tabnote}
    \Note{Note:}{Performance events that are obviously not indicative of any causal relationship are omitted, for example bus-cycles which will naturally vary with total cycle count.}
  \end{tabnote}
\end{table}

@@

% Table with detailed performance data, use estimated for O2 because it does not need as many columns (!)
\begin{table}[t]
  %\renewcommand{\tabcolsep}{3pt} % Less padding between cells
  \tbl{Most interesting performance counters and correlation with cycle count for optimization O2, estimated cost accounting for constant overhead.\label{tab:convstats}}{
    \pgfplotstabletypeset[
      %font=\footnotesize,
      int detect, % Output whole numbers for counter values
      col sep=comma,
      columns={Performance counter, Correlation, 0, 2, 4, 8},
      column type=r,
      columns/Performance counter/.style={
        string type, 
        column type=l,
        column type/.add={|}{},
        postproc cell content/.append code={
          \pgfkeysalso{@cell content=\perfctr{##1}}
        }
      },
      columns/Correlation/.style={
        fixed,
        fixed zerofill,
        precision=2
      },
      every head row/.style={
        output empty row,
        before row={\hline
          Performance counter & $r$ & 0 & 2 & 4 & 8 \\
        },
        after row=\hline\hline
      },
      every last row/.style={after row=\hline},
      every last column/.style={column type/.add={}{|}}
    ]{bin/conv-default-o2.estimate.csv}
  }
\end{table}

@@

\begin{table}[t]
  \centering
  \label{tab:mallocompare}
  %\renewcommand{\tabcolsep}{4pt} % Less padding between cells
  \tbl{Addresses returned by different heap allocators when allocating pairs of equally sized buffers.}{
    \pgfplotstabletypeset[
      col sep=comma,
      string type,
      columns={Allocation, 64, 5120, 1048576},
      column type=r,
      columns/Allocation/.style={
        string type, 
        column type=l,
        column type/.add={|}{}
      },
      every head row/.style={
        output empty row,
        before row={\hline
           & 64 B & 5,120 B & 1,048,576 B \\
          },
        after row=\hline\hline,
      },
      every last row/.style={after row=\hline},
      every last column/.style={column type/.add={}{|}},
      every odd row/.style={after row=\hline},
    ]{bin/malloc-comparison.csv}
  }
\end{table}
